---
title: "Assignment 9"
author: "Abdaljbbar Dawod"
date: "`r Sys.Date()`"
output: html_document
---
```{r}
library(astsa)
library(forecast)
plot.ts(oil, xlab = "Time",ylab="oil prices ($)", main = "Crude oil prices in dollars per barrel")
```

Differencing may be necessary for the data in the above plot due to its noticeable upward trend.

Plotting the ACF and PACF of the data yields:

```{r}
acf2(oil, 25)
```

It is clear from the ACF and PACF that the series is not stationary as ACF is decaying very sloly 

We then create a differenced data to make the data stationary on the mean and remove the trend

```{r}
plot(diff(oil),ylab="oil prices ($)", main = 'Differenced Crude oil prices')
```

The plot looks good, but there is increase in the variance of the series. Hence, we should take log transformation before the differencing.

```{r}
plot(diff(log(oil),1), ylab = 'Diff(Log(Price))')
acf2(diff(log(oil),1))
```


```{r}
plot(diff(log(oil),2), ylab = 'Diff(Log(Price),2)')
acf2(diff(log(oil),2))
```


```{r}
(fit.1 <- arima(log(oil), order=c(0,2,1)))
tsdiag(fit.1)
qqnorm(resid(fit.1))
qqline(resid(fit.1), datax = FALSE, distribution = qnorm, col='red')
```


```{r}
(lamda <- BoxCox.lambda(oil))

g <-BoxCox(oil, lamda)
acf2(diff(g,1))
#auto.arima(diff(g,1))
(fit.2 <- arima(g, order=c(1,1,3),seasonal = list(order=c(1,0,1))))
#tsdiag(fit.2)
```


